Generating Simulated Data

### 2021-05-24 docs/SimData.Rmd
fix readlines code blocks, update html

```{r, code = readLines(here("/simulated-data/config/NOBA2Config.R")), eval=F}
```

@@

```{r, code = readLines(here("/simulated-data/config/omdimensions.R")), eval=F}
```

@@

```{r, code = readLines(here("/simulated-data/config/mssurvey_spring.R")), eval=F}
```

```{r, code = readLines(here("/simulated-data/config/mssurvey_fall.R")), eval=F}
```

@@

```{r, code = readLines(here("/simulated-data/config/msfishery.R")), eval=F}
```

>>>>

```{r, code = readLines(here("simulated-data/config/NOBA2Config.R")), eval=F}
```

@@

```{r, code = readLines(here("simulated-data/config/omdimensions.R")), eval=F}
```

@@

```{r, code = readLines(here("simulated-data/config/mssurvey_spring.R")), eval=F}
```

```{r, code = readLines(here("simulated-data/config/mssurvey_fall.R")), eval=F}
```

@@

```{r, code = readLines(here("simulated-data/config/msfishery.R")), eval=F}
```
